Making Sequential Programs Deterministic

### 2019-03-31 experiments.tex
Fix cross-reference

We ran NonDex on the same commit of Randoop as we used for the case study
of \cref{sec:case-study}.  This version contains 3 nondeterminism bugs that
\theDeterminismChecker found.

@@

\TheDeterminismChecker is also capable of detecting nondetermism in test cases. We provide a stub file
for \<junit> in which we annotated all the \<assert> methods as accepting only \<Det> parameters.
This will report any \<junit> test that passes nondeterministic arguments to \<assert>s and the test doesn't
even have to be executed in our case.
\todo{It took one of our authors about an hour to create this stub file - proof of easy extensibility of tool?} 
\todo{Link to det checker repo?}

>>>>

We ran NonDex on the same commit of Randoop as we used for the case study
of \cref{sec:randoop-case-study}.  This version contains 3 nondeterminism bugs that
\theDeterminismChecker found.

@@

\TheDeterminismChecker is also capable of detecting nondetermism in test cases. We provide a stub file
for \<junit> in which we annotated all the \<assert> methods as accepting only \<Det> parameters.
This will report any \<junit> test that passes nondeterministic arguments to \<assert>s and the test doesn't
even have to be executed in our case.
\todo{It took one of our authors about an hour to create this stub file - proof of easy estensibility of tool?} 
\todo{Link to det checker repo?}
